Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 method.tex
Added asymptotic expression for fd flop/s
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1115 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

In the limit of many templates, $M \gg 1$, we may neglect the cost of the forward
transform of the data and of the multiplication of the transforms.  By making the common
choice of an \fft\ block size of twice the length of the filter,
$\fftblock = 2 \tmpsamps$, this simplifies to $\approx 4 f^0 \numtmps \lg \fftblock$
\flops.
